### 2015-04-01 README.Rmd
Small addition.
grammar
I Admire your politness but told you : I am a defender of the alphabetical order :)

[Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University) and [John J. Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University).

@@

>>>>

[John J. Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University)
 and [Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University).

@@

The colors of the nodes correspond to different beliefs about the climate.
